---
title: "Vignette of rGMAP package"
author: "Wenbao Yu"
date: "rGMAP version 1.3.1 <br><br>Updated on `r Sys.Date()`"
output: BiocStyle::html_document
mainfont: Arial
vignette: >
 %\VignetteIndexEntry{rGMAP}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = F, message = F,
  comment = "#>"
)
```

# Introduction
* rGMAP is an R package for implementing GMAP algorithm for detecting topologically associating domains (TADs) and sub-domains (sub-TADs)
* The detailed of the algorithm can be found in *Yu, W., He, B., & Tan, K. (2017). Identifying topologically associating domains and subdomains by Gaussian Mixture model And Proportion test. Nature Communications, 8, 535*

# Update for this version
* hic_mat could either be a data.frame/matrix or a text file for a Hi-C contact matrix
* Support multiple chromosomes if index file was also provided. The index_file and hic_mat are compatible to output of HiC-Pro
* If the input hic_mat is just from a sigle chromosome and no index_file was provided: the first two columns should be the i_th, j_th bin of the chromosome if hic_mat is in 3-column format (**i j count**)
* n by n matrix of hic_mat is still supported, where n is the total number of bins of a hic contact map for a single chromosome



# Installation
## Install from Github
```{r}
library(devtools)
install_github('wbaopaul/rGMAP')

```

## Install from source codes
```{r, eval=F}

install.packages('path to rGMAP_1.3.1.tar.gz', repos = NULL, type = 'source')

```

# Examples
## Work on an published Hi-C data
> Data from *Rao et al., Cell 2014, A 3D map of the human genome at kilobase resolution reveals principles of chromatin looping*

> KR normalized Hi-C data for IMR90 cell line, on chr15 with resolution 10kb

```{r, fig.height=3, fig.width=15, fig.align='center'}
library(rGMAP)
hic_rao_IMR90_chr15   
res = rGMAP(hic_rao_IMR90_chr15, resl = 10 * 1000, dom_order = 2)
names(res)

#quickly visualize some hierarchical domains
pp = plotdom(hic_rao_IMR90_chr15, res$hierTads, 5950, 6900, 30, 10000)
pp$p2

```


## Compatible with HiC-Pro output matrix and index file
* The format of the hic_mat data:

```
10	127	10.372577
10	188	4.161271
10	281	36.072713
17	5822	2.418056
......

```

* The format of the index file (10kb for example):

```
chr1	0	10000	1
chr1	10000	20000	2
chr1	20000	30000	3
chr1	30000	40000	4
......
```


## Work on an simulated example
```{r, fig.height=3, fig.width=15, fig.align='center'}
set.seed(1)
simu_res = data_simu('poisson-dist-hier')
true_domains = simu_res$hierTads
simu_mat = simu_res$hic_mat
predicted_domains = rGMAP(simu_mat, resl = 1)$hierTads

pp = plotdom(simu_mat, predicted_domains, 1, 1000, 20, 1)
pp$p2

#true_domains
#predicted_domains


```


# Session Information
```{r}
session_info()
```
